Open-Set Domain Adaptation through Self-Supervision

### 2022-02-11 paper/main.tex
small fix v2

{\it Relative orientation:}
more precisely, we exploit a relative rotation task,
implying that both the features of the original and rotated image are supplied to the rotation classifier.
This is preferred over the absolute rotation task as some objects might not have an absolute coherent orientation
inside the dataset
(e.g. a pen may be present in different rotated versions inside the dataset).

>>>>

{\it Relative orientation:}
more precisely, we exploit a relative rotation task,
which implies that both the features of the original and rotated image are supplied to the rotation classifier.
This is preferred over the absolute rotation task as some objects might not have an absolute coherent orientation
inside the dataset
(e.g. a pen may be present in different rotated versions inside the dataset).
